### 2024-02-04 README.Rmd
improve readme

1.  As an aid to setting up contiguity structures, particularly when islands are involved, the package has a function to quickly map any contiguity structure for visual inspection. This can also be used to examine the output of `sfdep` contiguity functions. Such maps can be used to check if the structure makes sense, given the researcher's knowledge about the geography of the study area.

2.  If there are some contiguities present which are not appropriate, or if you wish to add additional ones, there are functions to allow this to be done in a straightforward and openly reportable way.

3.  Once an appropriate neighbourhood structure is in place, different types of statistical tests and models can be performed. `sfdep` contains functionality to perform such test, and the output from `sfislands` can be used in its functions.

4.  The contiguity outputs from `sfislands` can be directly used to fit different types of (multilevel) (I)CAR models using, for example, the `mgcv`, `brms`, `stan` or `INLA` packages.

5.  For `mgcv` in particular, the predictions of such models can be quite tedious to extract and visualise. `sfislands` can streamline this workflow from the human side. Furthermore, there is a function to draw maps of these predictions for quick inspection.

@@

The following is a framework within which these functions could be used:

>>>>

1.  The initial setting up neighbourhood structures can be frustrating for people who are eager to get started with fitting spatial models. This is especially so when the presence of discontiguities within a geographical dataset means that, even having set up a neighbours list,  the model will still not run without further awkward data manipulations.

2.  As an aid to setting up contiguity structures, particularly when islands are involved, the package has a function to quickly map any contiguity structure for visual inspection. This can also be used to examine the output of `sfdep` contiguity functions. Such maps can be used to check if the structure makes sense, given the researcher's knowledge about the geography of the study area.

3.  If there are some contiguities present which are not appropriate, or if you wish to add additional ones, there are functions to allow this to be done in a straightforward and openly reportable way.

4.  Once an appropriate neighbourhood structure is in place, different types of statistical tests and models can be performed. `sfdep` contains functionality to perform such test, and the output from `sfislands` can be used in its functions.

5.  The contiguity outputs from `sfislands` can be directly used to fit different types of (multilevel) (I)CAR models using, for example, the `mgcv`, `brms`, `stan` or `INLA` packages.

6.  For `mgcv` in particular, the predictions of such models can be quite tedious to extract and visualise. `sfislands` can streamline this workflow from the human side. Furthermore, there is a function to draw maps of these predictions for quick inspection.

@@

The following is a framework within which the `sfislands` functions could be used:
